---
title: Running basic analyses on Pilot Data
author:
  # see ?rjournal_article for more information
  - name: Daniela Gawehns
    affiliation: Liacs Leiden University
    address:
    - line 1
    - line 2
    url: https://journal.r-project.org
    orcid: 0000-0002-9079-593X
    email:  author1@work
  - name: Matthijs van Leeuwen
    url: https://journal.r-project.org
    email: author2@work
    orcid: 0000-0002-9079-593X
    affiliation: Liacs Leiden University
    address:
    - Niels Bohr Weg 1
    - Leiden, Netherlands
    affiliation2: Affiliation 2
    address2:
    - line 1 affiliation 2
    - line 2 affiliation 2

abstract: >
  Supplementary Material to "Social Fluidity in Children's Face-to Face Interaction Networks"
preamble: |
  % Any extra LaTeX you need in the preamble
  
# per R journal requirement, the bib filename should be the same as the output 
# tex file. Don't forget to rename the bib file and change this example value.
bibliography: RJreferences.bib

output: rticles::rjournal_article
---

```{r}
library(ggplot2)
```



## Data Cleaning and Exporting as .txt file

The pilot data is included in the package and is formatted into .txt files with the help of a couple of functions.

```{r, echo = FALSE,, warning=FALSE}
# Create data .txt 
setwd("~/fluiditypilot/analysis/data/raw_data")
infoPilot2_40_1<-fluiditypilot::get.txt.files(binsize=2, minlength=40, minlag=1,group = "Pilot")
infoPilot2_20_1<-fluiditypilot::get.txt.files(binsize=2, minlength=20, minlag=1,group = "Pilot")
infoPilot2_10_1<-fluiditypilot::get.txt.files(binsize=2, minlength=10, minlag=1,group = "Pilot")

```
The created .txt files can be used within the jupyter notebook to estimate phi and get an overview of several network metrics. 

We cannot share the raw data of the data collection with children. 
We can however share the derived phi values without a mention of classrooms, schools or time of the day or time of data collection. 

## Use processed data to create plots

Create plots with phi values, as in Fig. 4 of the GEM Paper, showing the spread of $\phi$ values.

```{r, echo=FALSE, warning=FALSE}
# one dot per network for phi
# boxplots showing spread of phi per cut-off value:
setwd("~/fluiditypilot/analysis/data/derived_data")
dat.frame.results <- utils::read.csv("resultsGEMPaperFig4.csv", header = TRUE, stringsAsFactors = FALSE)
#dat.frame.results <- dat.frame.results [-1,]

fill <- "grey"
lines <- "black"

p10 <- ggplot(dat.frame.results, aes(x = as.factor(cutoff), y = dat.frame.results$round.PhiValue..3.)) +
        geom_boxplot(alpha= 0.8,colour = lines, fill = fill,
                     size = 1) +
      #  geom_point(aes(fill = fill), colour = lines, size = 1, shape = 2, position = position_jitterdodge()) +
        scale_y_continuous(name = "Phi Values",
                              breaks = seq(0, 1.2, 0.2),
                              limits=c(0, 1.2)) +
        scale_x_discrete(name = "Minimum Length of Interaction") +
        #ggtitle("Distribution of Phi Values per cut off score for \"minimum interaction length\" ") +
        theme_bw() #+

p10 <- p10 + geom_jitter(width=0.1)

p10

```




